Follow-up Samples

### 2016-12-05 submission/supplemental_outline_20161024.Rmd

source('code/functions.R')
source('code/graphFunctions.R')

loadLibs(c("pROC","randomForest","AUCRF", "Boruta", "dplyr", "tidyr", "ggplot2", "reshape2", 
           "gridExtra", "scales", "wesanderson", "vegan", "knitr"))

@@

alpha_table <- read.csv("results/tables/alpha_table_summary.csv", header = T, stringsAsFactors = F)
supplemental_table1 <- separate(alpha_table, X, c("comparison", "alpha_metric"), sep="_")

@@

imp_model_vars <- read.csv('results/tables/rf_wCV_imp_vars_summary.csv', stringsAsFactors = F, header = T)
rf_otu_tax <- read.csv('results/tables/rf_otu_tax.csv', stringsAsFactors = F, header = T, row.names = 1)
rf_otu_tax <- cbind(otu = rownames(rf_otu_tax), rf_otu_tax)

@@

follow_up_prob_summary <- read.csv('results/tables/follow_up_probability_summary.csv', stringsAsFactors = F, header = T)

@@

pvalue_common_imp_vars <- read.csv('results/tables/pvalue_common_imp_vars.csv', header = T, row.names = 1)

@@

diff_table_time <- read.csv("results/tables/time_datatable.csv", header = T)

@@

ggsave(file = "results/figures/FigureS1.pdf", time_graph, 
       width=6, height = 8, dpi = 300)
```

>>>>

source('../code/functions.R')
source('../code/graphFunctions.R')

loadLibs(c("dplyr", "tidyr", "ggplot2", "reshape2", "gridExtra", "scales", "wesanderson", "knitr", "rmarkdown"))

@@

alpha_table <- read.csv("../results/tables/alpha_table_summary.csv", header = T, stringsAsFactors = F)
supplemental_table1 <- separate(alpha_table, X, c("comparison", "alpha_metric"), sep="_")

@@

imp_model_vars <- read.csv('../results/tables/rf_wCV_imp_vars_summary.csv', stringsAsFactors = F, header = T)
rf_otu_tax <- read.csv('../results/tables/rf_otu_tax.csv', stringsAsFactors = F, header = T, row.names = 1)
rf_otu_tax <- cbind(otu = rownames(rf_otu_tax), rf_otu_tax)

@@

follow_up_prob_summary <- read.csv('../results/tables/follow_up_probability_summary.csv', stringsAsFactors = F, header = T)

@@

pvalue_common_imp_vars <- read.csv('../results/tables/pvalue_common_imp_vars.csv', header = T, row.names = 1)

@@

diff_table_time <- read.csv("../results/tables/time_datatable.csv", header = T)

@@

ggsave(file = "../results/figures/FigureS1.pdf", time_graph, 
       width=6, height = 8, dpi = 300)
```
